Parsing Tweets into Universal Dependencies

### 2017-11-27 paper.tex
Noah done for now

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over \nascomment{which?} the baseline
and outperforms parsers that are state-of-the-art on other treebanks.
\end{abstract}

@@

To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of a 20-parser
ensemble. \nascomment{return to this and clarify}
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show that an improvement of more
than 2.3 points in LAS over the baseline parser can be achieved with our
distillation method and it outperforms other state-of-the-art parsers.

@@

\item We introduce and evaluate a system to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}).  \nascomment{say it
  performs better than existing systems?}
\item We propose a new distillation
method for training the parser in our pipeline,  which achieves 2.3 points improvement in LAS
without sacrificing efficiency and outperformed other state-of-the-art parsers
in our comparison. \nascomment{clean up, remove redundancies with
  previous paragraph}
\end{itemize}

@@

\yjcomment{I've add the source of our example in the figure caption.}
\section{Annotation}\label{sec:anno}
\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}

@@

\subsection{Tokenizer} \label{sec:tok}
Tokenization, as the initial step of many NLP tasks, is non-trivial for
informal tweets, which include hashtags, at-mentions, and emoticons
\cite{ICWSM101540}.  Context is often required for tokenization
decisions; for example,
the asterisk (*) in {\it 4*3} is a separate token signifying
multiplication, but for the asterisk (*) in {\it sh*t}
works as a mask for censorship and should not be segmented.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		Stanford CoreNLP & 96.6 \\
		Twokenizer & 94.4 \\
% 		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 (same training data) & 97.3 \\
		Our bi-LSTM tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

We trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training dataset
and tested on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
The Stanford \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system.
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems and also two bi-LSTM systems similar
to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use the twitter specific glove embedding released by
\citet{pennington-socher-manning:2014:EMNLP2014} as the word embeeding in all the neural tagger
and parser\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}.

\nascomment{I wonder if we ought to give more detail about our biLSTM
  systems, here and under tokenization?  will reviewers want to know details?}
\yjcomment{I add figure to illustrat our model.}

@@

We tested the POS taggers on \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
models.  (That tagger also makes use of \citet{Brown:1992:CNG:176313.176316} clusters derived
from a large collection of unannotated tweets.  Those clusters did not
improve the performance of our bi-LSTM models.)

@@

Social media applications typically require processing large volumes
of data, making speed an important criterion. We therefore 
use the neural greedy parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
which can parse a sentence in linear time and harnesses 
character representations, which should help mitigate the challenge of
spelling variation. We encourage the reader to refer their paper for
more details about the model.

Section \ref{sec:anno-process} shows that severe ambiguities
exist when we create {\sc Tweebank v2}, which makes the training data
of the parser very noisy. \citet{Frnay2014ClassificationIT} suggested
that most of losses are shown to be not robust to 
classification noise, including the log-likelihood loss used in
\citet{ballesteros-dyer-smith:2015:EMNLP}. To conquer the noisy
data and further improve the parsing accuracy, we followed the
empirical study of \citet{Dietterich2000} and ensemble of 20 differently
initialized parsers. To make it still parses in linear time, we
propose a new method to distill the ensemble of 20 parsers into one parser.
To our knowledge, this is the first attempt to distill an
ensemble of greedy transition-based
parsers.% \nascomment{check}.

Distilling a simple and fast {\it student model} from the accurate but
slow {\it teacher model} was explored by \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016}. In their works, the predicted
distribution from the teacher model serves as a soft target for
training the student model by minimizing
\begin{equation}
\mathcal{L}_{\mathit{KD}} = \sum_k q(y=k\mid x) p(y=k\mid x)
\end{equation} where $q(y=k\mid x)$ is the probability distribution
predicted by the teacher model. Training the parameters of the student model ($p$) is
accomplished by interpolating between two losses:
\begin{equation}\label{eq:distill}
\mathcal{L}=(1-\alpha)\mathcal{L}_{\mathit{NNL}} + \alpha\mathcal{L}_{\mathit{KD}}
\end{equation}
where $\mathcal{L}_{\mathit{NNL}}$ is the negative log-likelihood loss.

\newcite{kuncoro-16} were inspired by the distillation idea and
proposed to incorporate the knowledge from an ensemble of 20 greedy transition-based
parsers into one single \emph{graph-based} parser by adapting the soft
target into a structured loss. However, as \newcite{kuncoro-16}
pointed out, it is not straightforward to incorporate the structure
loss into a \emph{transition-based} parser. Considering the efficiency
advantage of greedy transition-based parsers over their graph-based counterparts,
it is worth considering distillation of an ensemble into a greedy parser.

The generic algorithm for training a transition-based greedy parser
usually includes 1) generating a sequence of transitions from the 
training data, called the ``oracle'' and 2) learning the classifier from
the oracle transitions. One natural adaptation of the distillation will be interpolating
$\mathcal{L}_{\mathit{NLL}}$ with the distillation objective (Equation \ref{eq:distill})
in the second step. We name this method \textsc{distill expert}.

\paragraph{Preliminary results.}
In our preliminary experiments, we train our parser on the combination of UD\_English
and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
tags are used. Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
labeled attachment score including punctuations are used to evaluate parsing performance.

\citet{reimers-gurevych:2017:EMNLP2017} pointed out that the training process for neural networks are highly
non-deterministic and largely depends on the seed value for pseduo-random number generator.
Our preliminary experiments confirm this finding by witnessing a gap of 1 LAS on development set
between the best (75.8) and worst (74.8) runs. To eliminate the effect of random number, for each
hyperparameter setting, we conduct 5 runs with different seeds and report the averaged score.

Our 20 parsers are ensembled by averaging their output probability
distributions over transitions. The ensemble parser achieves a LAS of 79.4, which is more 
than 3 points higher than the baseline single parser. Distilling from this
parser leads to a single parser with 78.1 LAS.
%We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).

\paragraph{Effect of $\alpha$.}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
	\caption{The effect of $\alpha$ on \textsc{expert distillation}.}\label{fig:effect-alpha}
\end{figure}

We further study the effect of the interpolation hyperparameter $\alpha$ by varying it from 0 to 1.
The results are shown in Figure \ref{fig:effect-alpha}. We can see that distilling parsers with larger $\alpha$ achieves better
performance, which means the model should pay more attention to learning
from the teacher model.  Indeed, the negligible difference between the
best performance at $\alpha = 0.9$ and $\alpha=1.0$ casts doubt on the
necessity of including $\mathcal{L}_{NNL}$ in the training objective
at all.% \nascomment{check my rewording}

\paragraph{Learning from exploration.} We further set $\alpha$ to 1.0,
eliminating the oracle from the usual transition-based parser
training algorithm.  Instead of generating
training instances from the oracle, we generate them by random sampling
transitions from the teacher (ensemble) model's output distribution and follow the
trajectory of these transitions. We name this method \textsc{distill explore}.

\paragraph{Final results.}
\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 \\
		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 \\
		\hdashline
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
		Ensemble (20) & 83.5 & 79.4 \\
		\textsc{distill expert} ($\alpha$=1.0) & 82.2 & 78.0 \\
		\textsc{distill expert} ($\alpha$=0.9) & 82.4 & 78.1 \\		
		\textsc{distill explore} & 82.5 & 78.4 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. \label{tbl:parse-result}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{kuncoro-16} & 94.3 & 92.1 \\
		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
		\hdashline
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 94.5 & 92.6 \\
		\textsc{distill expert} ($\alpha$=1.0) & 93.8 & 91.7 \\
		\textsc{distill explore} & 94.1 & 92.0 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
\end{table}

Our final parsing experiments are shown in Table \ref{tbl:parse-result}.
We also compare our model with the {\sc TweeboParser} 
of \citet{kong-EtAl:2014:EMNLP2014} and the state-of-the-art parser
 \cite{DBLP:journals/corr/DozatM16} in CoNLL 2017.
Both the compared systems are re-trained on the same data as our system.
From Table \ref{tbl:parse-result}, our baseline system is 1.9 point behind the
state-of-the-art parsing systems. However, through distilling, our baseline
parser catched up and outperform that of \citet{DBLP:journals/corr/DozatM16} and 
\textsc{distill explore} further outperforms \textsc{distill expert}, gaining 0.4
point in LAS improvement. We attribute the improvements of \textsc{distill explore} over
\textsc{distill expert} to the former's exploration of 
ensemble-sanctioned parser states of different qualities.

We also perform additional experiments on the Penn Treebank were performed following
the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
performance close to that of the graph-based parser of \citet{kuncoro-16}.
However, our model is still way behind \citet{DBLP:journals/corr/DozatM16}.
We address this to the intrastic differences between transition-based and graph-based
parsing algorithm.

\subsection{Final Evaluation}
\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it Pipeline & F-score \\
		\hline
		Tokenization & 98.3 \\		
		POS tagging & 93.7 \\
		Dependencies & 74.1 \\
		\hline
	\end{tabular}
	\caption{Evaluating our model in pipeline manner.}\label{tbl:pipline}
\end{table}

Finally, we evaluate the problem of parsing tweets into UD in a pipeline manner.
The results are shown in Table \ref{tbl:pipline}. From this result, we can see
that in the whole pipeline, every component plays an important role. Without
gold segmentation, the parsing performance drops more than 4 points.

@@

\section{Conclusion}
In this paper, we study the problem of parsing tweets into universal dependencies.
We adopt the UD guidelines to cover 
special constructions in tweets and create
the {\sc Tweebank v2} which has 55,607 tokens. We characterize the disagreements
among our annotations and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. On this new treebank,
we build a pipeline system to parse tweets into UD. We 
propose a new method to distill an ensemble of 20 parsers into a single one
to conquer the annotation noise without sacrificing efficiency.
Our parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.

>>>>

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over \nascomment{which
  comparison is this?} the baseline
and outperforms parsers that are state-of-the-art on other treebanks.
\end{abstract}

@@

To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.3 points \nascomment{again, not sure what this is quoting} in LAS over the baseline parser can be achieved with our
distillation method and that it outperforms other state-of-the-art parsers.

@@

\item We introduce and evaluate a system to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}).  \nascomment{say it
  performs better than existing systems?}
\item We propose a new distillation
method for training a greedy parser, leading to better performance
than existing methods and without efficiency sacrifices.
\end{itemize}

@@

\section{Annotation}\label{sec:anno}
\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}

@@

\subsection{Tokenizer} \label{sec:tok}
Tokenization, as the initial step of many NLP tasks, is non-trivial for
informal tweets, which include hashtags, at-mentions, and emoticons
\cite{ICWSM101540}.  Context is often required for tokenization
decisions; for example,
the asterisk in {\it 4*3} is a separate token signifying
multiplication, but for the asterisk in {\it sh*t}
works as a mask to evoke censorship and should not be segmented.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{lr}
		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 96.6 \\
		 Twokenizer & 94.4 \\
% 		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 & 97.3 \\
	 	our bi-LSTM tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

We trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training dataset
and tested on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. \nascomment{we need to say what their model was;
  why does ours work better?  from their paper, it seems that they
  used a GRU instead of an LSTM ... is that all?  do we win because of
better tuning, or what?}
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems and also two bi-LSTM systems similar
to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use Twitter-specific glove embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
models.  (That tagger also makes use of \citet{Brown:1992:CNG:176313.176316} clusters derived
from a large collection of unannotated tweets.  Those clusters did not
improve the performance of our bi-LSTM models.)

@@

Social media applications typically require processing large volumes
of data, making speed an important desideratum. We therefore 
begin with the neural greedy stack LSTM parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
which can parse a sentence in linear time and harnesses 
character representations, which should help mitigate the challenge of
spelling variation. We encourage the reader to refer their paper for
more details about the model.

In our preliminary experiments, we train our parser on the combination of UD\_English
and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
tags are used. Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters %, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
labeled attachment score (including punctuation) are reported.

\citet{reimers-gurevych:2017:EMNLP2017} and others have
pointed out that neural network training is 
nondeterministic and depends on the seed for the random
number generator.
Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
between the best (75.8) and worst (74.8) runs. To control for this
effect, we report the average of five differently-seeded runs, for
each model. \nascomment{please check! we did this for all systems,
  not just ours, right?}

%%%

\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 \\
		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
		\hdashline
		Ensemble (20) & 83.5 & 79.4 \\
		Distillation ($\alpha =1.0$) & 82.2 & 78.0 \\
		Distillation ($\alpha =0.9$) & 82.4 & 78.1 \\		
		Distillation with exploration & 82.5 & 78.4 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. \label{tbl:parse-result}}
\end{table}

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
 parsers requiring superlinear runtime. \nascomment{can we quantify
   how much time each one takes, either in tweets parsed per second or
   seconds per tweet?}
Both of the comparison systems are re-trained on the same data as our
system.
Our system lags behind by nearly two LAS
points.

\paragraph{Ensemble.}  Due both to ambiguity in the training
data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
\citet{ballesteros-dyer-smith:2015:EMNLP}---and due to the instability
of neural network training, we follow \citet{Dietterich2000} and
consider an ensemble of twenty parsers trained using different random
initialization.  To parse at test time, the transition probabilities of the twenty
members of the ensemble are averaged.  The result achieves LAS of
79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).

\paragraph{Distillation.}  The shortcoming of the 20-parser ensemble is, of
course, that it requires twenty times the runtime of a single greedy
parser.  \newcite{kuncoro-16} proposed the distillation of 20
greedy transition-based parser into a single \emph{graph-based}
parser; they transformed the votes of the ensemble into a structured
loss function.  However, as Kuncoro et al.~pointed out, 
it is not straightforward to use a structured
loss in a \emph{transition-based} parsing algorithm.  Because fast
runtime is so important for NLP on social media, we
introduce a new way to distill our greedy ensemble into a single
transition-based parser (the first such attempt, to our knowledge).

Our approach follows \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016}.  
Note that training a transition-based parser typically involves the
transformation of the training data into a sequence of ``oracle'' state-action
pairs.
Let $q(a \mid s)$ denote the distilled model's
probability of an action $a$ given parser state $s$; let $p(a \mid s)$ be the probability under the
ensemble (i.e., the average of the 20 separately-trained ensemble
members) \nascomment{check}.
To train the distilled model, we minimize the interpolation between
their distillation loss and the conventional log loss:
\begin{align}
\min_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
  \mid s_i)}_{\text{distillation loss}} \\
& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
  s_i)}_{\text{log loss}} \nonumber
\end{align}

Distilling from this 
parser leads to a single greedy transition-based parser with 78.1
LAS---better than past systems but worse than our more expensive ensemble.
The effect of $\alpha$ is illustrated in
Figure~\ref{fig:effect-alpha}; generally paying closer attention to
the ensemble, rather than the conventional log loss objective, leads
to better performance.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
	\caption{The effect of $\alpha$ on distillation. \label{fig:effect-alpha}}
\end{figure}

\paragraph{Learning from exploration.} When we set $\alpha =1$, we
eliminate the oracle from the estimation procedure (for the distilled
model).  This presents an opportunity to learn with \emph{exploration}, by
randomly sampling transitions from the ensemble, found useful
in recent methods for training greedy models that use dynamic oracles
\citep{ballesteros-EtAl:2016:EMNLP2016}.  
We find that this
approach outperforms the  conventional distillation model, coming in
only one point behind the ensemble (last line of Table~\ref{tbl:parse-result}).

\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{kuncoro-16} & 94.3 & 92.1 \\
		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
		\hdashline
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 94.5 & 92.6 \\
		Distillation ($\alpha =1.0$) & 93.8 & 91.7 \\
		Distillation with exploration  & 94.1 & 92.0 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
\end{table}

\nascomment{need to clarify:  is this UD?} We perform additional experiments on the Penn Treebank, following
the settings of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
performance close to that of the graph-based parser of \citet{kuncoro-16}.
However, this greedy approach still lags behind the very strong
graph-based system of \citet{DBLP:journals/corr/DozatM16}.

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it Pipeline & $F_1$\\
		\hline
		Tokenization & 98.3 \\		
		POS tagging & 93.7 \\
		Universal dependencies & 74.1 \\
		\hline
	\end{tabular}
	\caption{Evaluating our model in pipeline
          manner. \nascomment{should this be ``F1''?  shouldn't the
            last line be LAS?}\label{tbl:pipline} }
\end{table}

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We see the
importance of segmentation:  without gold segmentation, UD parsing
performance drops by more than four points.

@@

\section{Conclusion}
We study the problem of parsing tweets into universal dependencies.
We adapt the UD guidelines to cover 
special constructions in tweets and create
the {\sc Tweebank v2}, which has 55,607 tokens. We characterize the disagreements
among our annotations and argue that inherent ambiguity in this genre
makes
consistent annotaiton a challenge.  Using this new treebank,
we build a pipeline system to parse tweets into UD. We also 
propose a new method to distill an ensemble of 20 greedy parsers into a single one
to overcome annotation noise without sacrificing efficiency.
Our parser achieves an improvement of 2.3  \nascomment{which
  comparison are you quoting here?} in LAS over a strong baseline
and outperforms other state-of-the-art parsers.
